### 2019-08-14 Writeup/Thesis/pages/experiments.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

\section{Experiment 1 - Metric performance}
As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

@@

Overall, 104 participants were assessed in this study. Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having having too low of a fluency rating. This was a necessary process to improve the health of the results.

Figure \ref{tab:exp1_results} shows the average results for the metrics. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much larger proportion of 4 and 5 ratings than the alternatives alongside a very low level of low ratings. This performance may, however, be due to the visual way the comparisons are being performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

@@

Even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. The results are also an improvement over informal ad-hoc methods. Further work could aim to reproduce this study with the proposed audio based design.

@@

\section{Experiment 2 - Trustword attacks}
\label{sec:exp2}

Section \ref{sec:exp2_design} explains the design of the experiment. This section will present and discuss the results of the experiment alongside a comparison to relevant literature.

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This makes this set of participants more educated that the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.09\% \\
        Firefox & 12.20\% \\
        Safari & 1.90\% \\
        Other & 0.81\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%. The best performer when regarding attack strength, as expected is the 2 static words. Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%. The worst performer was Metaphone with an average of 16.88\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the exactly same order.

\begin{table}
    \centering
    \begin{tabular}{|ll|l|l|l|}
        \hline
        \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
        \hline
        Levenshtein && 218 & 1101 & 19.80\% \\
        \hline
        & 0 static   & 34  & 358  & ~9.50\% \\
        & 1 static   & 59  & 353  & 16.71\% \\
        & 2 static   & 125  & 390  & 32.05\% \\
        \hline\hline
        Metaphone &&  181 & 1072 & 16.88\% \\
        \hline
        & 0 static   & 38 & 345 & 11.01\% \\
        & 1 static   & 57 & 375 & 15.20\% \\
        & 2 static   & 86 & 352 & 24.43\% \\
        \hline\hline
        NYSIIS &&  209 & 1114 & 18.76\% \\
        \hline
        & 0 static   & 36 & 385 & ~9.35\% \\
        & 1 static   & 72 & 375 & 19.20\% \\
        & 2 static   & 101 & 354 & 28.53\% \\
        \hline\hline
        \textbf{Overall} & & 608 & 3287 & 18.50\% \\
        \hline\hline
    \end{tabular}
    \caption{Success rates for simulated attacks}
    \label{tab:exp2_attacks}
\end{table}

\subsection*{Considerations}
As previously mentioned, the set of recruited participants are more highly educated than the general population. This combined with the low average age contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment being a `best case' scenario. The attacks, therefore, would be expected to be more successful on less technical users. This, however, requires further research and possible empirical data to determine the validity of the assumption.

During this study the main task was to perform the authentication ceremony a large number of times. In the real-world the ceremony is a secondary task due to it not strictly being required. This alongside the potential for users to downplay the possibility of attack leads to the conclusion that the success rates could be much higher in a real-world setting. The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their authentication partner multiple times. This is opposed to the assumption that the majority of users will aim to complete the task as quickly as possible.

@@

Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success for the PGP Word list was 8.78\%. As 10/14 words were kept static more comparable to comparable the results to the highest attack strength ``2 static''. Therefore, there is another 3 fold improvement in the success rates of our simulated attacks.

The final relevant paper to compare is that of Tan \textit{et al.}. This paper had the highest number of words assessed with 16 overall. With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}. The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference.

@@

\begin{table}[!h]
    \centering
    \begin{tabular}{|lllll|}
        \hline
        \textbf{Metric} & & \textbf{Mean matches} & \textbf{$\sigma$} & \textbf{Compute Time} \\
        \hline
        NYSIIS &&&& \\
        \hline
        & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
        & 1 static & 448.37 & 4316.57 & 119.14 days \\
        & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
        \hline

@@

    \end{tabular}
    \caption{Each metric's average near-collision keys}
    \label{tab:average_perm}
\end{table}

As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible. On the other hand, Metaphone has attacks that could be computed on average in under 2 days. The success rate for this attack type in the second experiment was 11.01\% on average. This means on comity hardware commonly found in the home, an attacker could compute a key in less than two days that could succeed more than 10\% of the time. This is substantial and highlights on weaknesses in the Trustword system.

\section{Distribution of vulnerable keys}
\label{sec:vulnKeys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}. 100,000 random key pair were created and used as the sample. Any vulnerable keys in this set were recorded and used in the experiment.

@@

\begin{table}[!h]
    \centering
    \begin{tabular}{|lll|}
        \hline
        \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
        \hline 
        2 static (152) && \\ 
        & Levenshtein & ~~4.295\% \\
        & Metaphone & 24.095\% \\
        & NYSIIS & 10.441\% \\
        \hline
        1 static (1525) && \\ 
        & Levenshtein & ~~0.827\% \\
        & Metaphone & 15.569\% \\
        & NYSIIS & ~~4.341\% \\
        \hline
        0 static (15250) && \\ 
        & Levenshtein & ~~0.157\% \\
        & Metaphone & 10.202\% \\
        & NYSIIS & ~~1.824\% \\
        \hline
    \end{tabular}
    \caption{Number of vulnerable keys per metric}
    \label{tab:vulnkeys}
\end{table}

@@

\section{Generation of keys}
\label{sec:key_gen}
To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static) a key was computed. NYSIIS was chosen as the selected metric. To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches, adds very little to this demonstration.

\begin{table}[h!]
    \begin{tabular}{|l|l|}
        \hline
        Potential near-collision keys & 142,296 \\
        Hashing speed & 4000 MH/s \\
        Estimated computation time & 9 hours \\
        Actual computation & 6.41 hours \\
        GPU Days & 0.52 \\
        \hline
        Original Trustwords & BELL GRIND ALGERIA ANNULI \\
        Actual Trustwords   & BOIL GRAND ALGER ANNUL \\
        \hline
    \end{tabular}
    \caption{NYSIIS - 0 static}
    \label{tab:nysiis0}

    \begin{tabular}{|l|l|}
        \hline
        Potential near-collision keys & 133,200 \\
        Hashing speed & 8000 MH/s \\
        Estimated computation time & 4.2 hours \\
        Actual computation & 5.12 hours \\
        GPU Days & 0.853 \\
        \hline
        Original Trustwords & ASSUMING SONOMA DENS KEENER \\
        Actual Trustwords   & ASSUMING SUMMON DENNI CONNOR \\
        \hline
    \end{tabular}
    \caption{NYSIIS - 1 static}
    \label{tab:nysiis1}

    \begin{tabular}{|l|l|}
        \hline
        Potential near-collision keys & 16,464 \\
        Hashing speed & 6000 MH/s \\
        Estimated computation time & 2.16 days \\
        Actual computation & 23.44 hours \\
        GPU Days & 2.93 \\
        \hline
        Original Trustwords & VOCATION BORE TANN ANTE \\
        Actual Trustwords   & VOCATION BARE TONE ANTE \\
        \hline
    \end{tabular}
    \caption{NYSIIS - 2 static}

    \label{tab:nysiis2}
\end{table}

@@

As it can be seen most notable from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users. This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.

>>>>

\section{Experiment 1 - Metric performance}
\todo{talk about participants like the second experiment with Stdev}

As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

@@

Overall, 104 participants were assessed in this study. Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating. This was a necessary process to improve the health of the results.

Figure \ref{tab:exp1_results} shows the average results for the metrics. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much larger proportion of 4 and 5 ratings than the alternatives. This performance may, however, be due to the visual way the comparisons are being performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

@@

Even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. The results are also an improvement over informal ad-hoc methods. Further work could aim to reproduce this study with the proposed audio based design (See Section \ref{sec:exp1_considerations}).

@@

\section{Experiment 2 - Trustword attacks}
\label{sec:exp2}
The aim of this experiment is to quantify the success rate of the proposed attack. Design details for this experiment can be seen in Section \ref{sec:exp2_design}. This section will present and discuss the results of the experiment alongside a comparison to relevant literature.

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This makes this set of participants more educated than the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.09\% \\
        Firefox & 12.20\% \\
        Safari & 1.90\% \\
        Other & 0.81\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%. The best performer when regarding attack strength, as expected is the 2 static words. Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%. The worst performer was Metaphone with an average of 16.88\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in exactly the same order.

\begin{table}
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|ll|l|l|l|}
            \hline
            \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
            \hline
            Levenshtein && 218 & 1101 & 19.80\% \\
            \hline
            & 0 static   & 34  & 358  & ~9.50\% \\
            & 1 static   & 59  & 353  & 16.71\% \\
            & 2 static   & 125  & 390  & 32.05\% \\
            \hline\hline
            Metaphone &&  181 & 1072 & 16.88\% \\
            \hline
            & 0 static   & 38 & 345 & 11.01\% \\
            & 1 static   & 57 & 375 & 15.20\% \\
            & 2 static   & 86 & 352 & 24.43\% \\
            \hline\hline
            NYSIIS &&  209 & 1114 & 18.76\% \\
            \hline
            & 0 static   & 36 & 385 & ~9.35\% \\
            & 1 static   & 72 & 375 & 19.20\% \\
            & 2 static   & 101 & 354 & 28.53\% \\
            \hline\hline
            \textbf{Overall} & & 608 & 3287 & 18.50\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Success rates for simulated attacks}
    \label{tab:exp2_attacks}
\end{table}

\subsection*{Considerations}
As previously mentioned, the set of recruited participants are more highly educated than the general population. This combined with the low average age contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario. The attacks, therefore, would be expected to be more successful on less technical users. This, however, requires further research and possible empirical data to determine the validity of the assumption.

During this study the main task was to perform the authentication ceremony a large number of times. In the real-world the ceremony is a secondary task due to it not strictly being required. This alongside the potential for users to downplay the possibility of attack leads to the conclusion that the success rates could be much higher in a real-world setting. The assumption is that these results display the success rate for extremely attentive users where they will make sure to double check with their authentication partner multiple times. This is opposed to the assumption that the majority of users will aim to complete the task as quickly as possible.

@@

Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success for the PGP Word list was 8.78\%. As 10/14 words were kept static more comparable to the results of the highest attack strength ``2 static''. This leads to another 3 fold improvement in the success rates of our simulated attacks.

The final relevant paper to compare is that of Tan \textit{et al.}\cite{tan2017can}. This paper had the highest number of words assessed with 16 overall. With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}. The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference.

@@

\begin{table}[!h]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|lllll|}
            \hline
            \textbf{Metric} & & \textbf{Mean matches} & \textbf{$\sigma$} & \textbf{Compute Time} \\
            \hline
            NYSIIS &&&& \\
            \hline
            & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
            & 1 static & 448.37 & 4316.57 & 119.14 days \\
            & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
            \hline

@@

        \end{tabular}
    }
    \caption{Each metric's average near-collision keys}
    \label{tab:average_perm}
\end{table}

As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible. On the other hand, Metaphone has attacks that could be computed on average in under 2 days. The success rate for this attack type in the second experiment was 11.01\% on average. This means on commodity hardware commonly found in the home, an attacker could compute a key in less than two days that could succeed more than 10\% of the time. This is substantial and highlights on weaknesses in the Trustword system.

\section{Distribution of vulnerable keys}
\label{sec:vulnKeys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}. 100,000 random key pairs were created and used as the sample. Any vulnerable keys in this set were recorded and used in the experiment.

@@

\begin{table}[!h]
    \centering

    \makebox[\textwidth][c]{

        \begin{tabular}{|lll|}
            \hline
            \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
            \hline 
            2 static (152) && \\ 
            & Levenshtein & ~~4.295\% \\
            & Metaphone & 24.095\% \\
            & NYSIIS & 10.441\% \\
            \hline
            1 static (1525) && \\ 
            & Levenshtein & ~~0.827\% \\
            & Metaphone & 15.569\% \\
            & NYSIIS & ~~4.341\% \\
            \hline
            0 static (15250) && \\ 
            & Levenshtein & ~~0.157\% \\
            & Metaphone & 10.202\% \\
            & NYSIIS & ~~1.824\% \\
            \hline
        \end{tabular}
    }
    \caption{Number of vulnerable keys per metric}
    \label{tab:vulnkeys}
\end{table}

@@

\section{Generation of keys}
\label{sec:key_gen}
To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static) a key was computed. NYSIIS was chosen as the selected metric. To expedite the process an initial search was performed for controlled keys that had the highest number of near-collisions, this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches, adds very little to this demonstration.

\begin{table}[h!]

    \makebox[\textwidth][c]{
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 142,296 \\
            Hashing speed & 4000 MH/s \\
            Estimated computation time & 9 hours \\
            Actual computation & 6.41 hours \\
            GPU Days & 0.52 \\
            \hline
            Original Trustwords & BELL GRIND ALGERIA ANNULI \\
            Actual Trustwords   & BOIL GRAND ALGER ANNUL \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - 0 static}
    \label{tab:nysiis0}

    \makebox[\textwidth][c]{    
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 133,200 \\
            Hashing speed & 8000 MH/s \\
            Estimated computation time & 4.2 hours \\
            Actual computation & 5.12 hours \\
            GPU Days & 0.853 \\
            \hline
            Original Trustwords & ASSUMING SONOMA DENS KEENER \\
            Actual Trustwords   & ASSUMING SUMMON DENNI CONNOR \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - 1 static}
    \label{tab:nysiis1}

    \makebox[\textwidth][c]{
        \begin{tabular}{|l|l|}
            \hline
            Potential near-collision keys & 16,464 \\
            Hashing speed & 6000 MH/s \\
            Estimated computation time & 2.16 days \\
            Actual computation & 23.44 hours \\
            GPU Days & 2.93 \\
            \hline
            Original Trustwords & VOCATION BORE TANN ANTE \\
            Actual Trustwords   & VOCATION BARE TONE ANTE \\
            \hline
        \end{tabular}
    }
    \caption{NYSIIS - 2 static}
    \label{tab:nysiis2}
\end{table}

@@

As it can be seen most notably from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users. This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.

### 2019-08-14 Writeup/Thesis/pages/implementation.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

GreenOnion is written in C++. This languages was chosen due to its efficiency bonuses over other alternative languages.
The tool begins by generating a 2048-bit RSA key through GPG\footnote{GNU Privacy Guard}. This key is then used to create a hash of all but the final 512-bit block of the key. The final block of the key is left un-hashed due to the presence of the exponent ($e$). This exponent is incremented to create a new unique key. This is the aspect provides rapid generation of new keys due to the reduction in expensive large prime generation. This prevents issues in such as entropy starvation when generating a large number of valid RSA keys. This produces valid keys but with abnormally large exponents, this was deemed as suitable due to the short term use-case for these keys. 3 bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for a single expensive key generation.

@@

Mass checking of fingerprints is the tools main abilities as it allows for millions of keys to be checked with a very small amount of overhead. This is achieved through the use of a bloom filter. A bloom filter is a probabilistic data structure that allows efficient checking for presence of an element in a set. It is effectively a very large array of booleans that state wether an element is present. The index in the array is decided by a pre-defined hashing algorithm. This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$). This then means checking the presence of an element in the set will just means hashing the target and checking the indices returned. This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set. This is the only data structure that provides this characteristic.

However, due to the random distribution of the hashing algorithms, there is the possibility for collisions and, thus, the possibility of false-positives. The data structure, however, does not produce any false-negatives. This, therefore, makes it fully suited to this use-case as any fingerprints tagged as ``possibility'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine their actual presence. Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$) the tool can search through huge number of potential keys without any decrease in speed.

@@

The \verb|<EXPONENT_INCREMENTING_CODE>| will be explained in the next section. After the exponent is increment the code produces the final digest by calling \verb|sha1_block(W, H)|. The 32-bit left and right sections of the digest are hashed using the MurmurHash algorithm. MurmurHash does not exhibit features suitable for secure hashing as it can be trivially reversed. Its use-cases include hash based lookups due to its speed and its distributive properties, making it suitable to work well with a bloom filter. The hashed values are then checked against the bloom filter array. If there is a possible match, the identification value (\verb|0x12345678|) is placed in the first byte of the \verb|outResult| alongside the exponent used to produce the possibly matching PGP key. The minimal amount of data returned to the CPU via the \verb|outResult| variable is due to efficiency reasons. Use of this memory is computationally expensive, therefore, at every opportunity writing or reading this memory has been avoided.

@@

Figure \ref{fig:increment} contains the code used to increment the exponent. Due to the exponent being split across two words alongside the bare bones functionality of OpenCL binary operations were chosen as the solution to the incrementation. The code utilise the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$. This will allow us to replace values using binary operations. The code manipulates the position of values by multiplication or division  of base-16 values, these shift the hex value either left of right respectively. Once it is in position the "Mask" is created by XORing with the original value and the new intended value, this stores the changes required to reach the required values, this then applied to each of the words.
The \verb|get_global_id| command takes the ID from the currently running thread, this allows a different value to be used for each exponent and allows the code to be run concurrently.

\section{First Experiment}
In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire. It provided functionality to easily present questions and record their responses. However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality a solution was required. This was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form. This allowed the re-sampling of matches each time a user submitted a response.

@@

Figure \ref{fig:GoogleAppScript} contains an interesting snippet from the script used in the experiment. Each time a user submitted their response the \verb|updateForm()| endpoint was called, that subsequently updated the questions for the next user. This aimed to keep the samplings fair as they are equality likely to appear when attacking the system alongside an ample exploration of the overall match quality.

\section{MainExperiment}
In order to asses users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required. The front-end is developed in Javascript with a Python-Flask backend that acts as the webpages functionality. A number of end points are exposed like \verb|get_audio| or \verb|get_words| that are requested and displayed on the front-end.

One of the main problems encountered was the handling of each user's session. Initially during testing it was noted that changes in one end-point if timed correctly would overwrite the progress of another, this is commonly know as a ``Lost update''. This was due to the user session being stored in the \verb|session| cookie. When sending off a request the session cookie is included in the header, the code will then utilise the data within the cookie to make decision and alter state, the updated state is then returned as a cookie in the response. If, however, another request is executed before the first has completed, the second request is using the context of the first request and, thus, any alterations made by the first will be completely lost.

@@

Figure \ref{fig:cookie} shows this problem visually. As it can be seen the response cookie $c_2$ is based of the old data of $c$ and, therefore, when returned will remove the progress of $c_1$. To keep the complexity of the backend low it was opted to solve this problem by restricting the user via the UI, when a button was clicked all other operations were disabled until a response was received. This stopped the possibility of sending off another request while another is still processing.

In order to collate data for results later in the process state had to be saved. One potential solution would be to format the data and save it as a .csv file. However, this is a static way of data persistence and would require alteration every time the data schema was modified. The chosen solution utilized a python object serialization library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}. This library saves the an instance of a class as a file. This file then can be used to load the instance of the class back into the program. This allows changes to the object to filter down through the program and keeps the design of the application fluid. For example, after initial feedback gathered about the application it was decided that a inclusion of `Round times' would be a useful addition. Edits were made to the \verb|experiment| class and the changes propagated through the application, no changes were needed on the save functionality. To distinguish between old and new save formats a version number was used.

>>>>

GreenOnion is written in C++. This language was chosen due to its efficiency bonuses over other alternative languages.
The tool begins by generating a 2048-bit RSA key through GPG\footnote{GNU Privacy Guard}. This key is then used to create a hash of all but the final 512-bit block of the key. The final block of the key is left un-hashed due to the presence of the exponent ($e$). This exponent is then incremented to create a new unique key. This allows rapid generation of new keys due to the reduction in expensive large prime generation. This prevents issues in such as entropy starvation when generating a large number of RSA keys. This produces valid keys but with abnormally large exponents, this was deemed as suitable due to the short term use-case for these keys. 3 bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for a single expensive key generation.

@@

Mass checking of fingerprints is the tools main ability as it allows for millions of keys to be checked with a very small amount of overhead. This is achieved through the use of a bloom filter. A bloom filter is a probabilistic data structure that allows efficient checking for presence of an element in a set. It is effectively a very large array of booleans that state wether an element is present. The index in the array is decided by a pre-defined hashing algorithm. This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$). This then means checking the presence of an element in the set just means hashing the target and checking the indices returned. This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set. This is the only data structure that provides this characteristic.

However, there is the possibility for collisions and, thus, the possibility of false-positives. The data structure, however, does not produce any false-negatives. This, therefore, makes it fully suited to this use-case as any fingerprints tagged as ``possibly'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine their actual presence. Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$) the tool can search through huge number of potential keys without any decrease in speed.

@@

The \verb|<EXPONENT_INCREMENTING_CODE>| will be explained in the next section. After the exponent is incremented the code produces the final digest by calling \verb|sha1_block(W, H)|. The 32-bit left and right sections of the digest are hashed using the MurmurHash algorithm. MurmurHash does not exhibit features suitable for secure hashing as it can be trivially reversed. Its use-cases include hash based lookups due to its speed and its distributive properties, making it suitable to work well with a bloom filter. The hashed values are then checked against the bloom filter array. If there is a possible match, the identification value (\verb|0x12345678|) is placed in the first byte of the \verb|outResult| alongside the exponent used to produce the possibly matching PGP key. The minimal amount of data returned to the CPU via the \verb|outResult| variable is due to efficiency reasons. Use of this memory is computationally expensive, therefore, at every opportunity writing or reading this memory has been avoided.

@@

Figure \ref{fig:increment} contains the code used to increment the exponent. Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations were chosen as the solution to the incrementation. The code utilise the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$. This will allow us to replace values using binary operations. The code manipulates the position of values by multiplication or division  of base-16 values, these shift the hex value either left of right respectively. Once it is in position the "Mask" is created by XORing with the original value and the new intended value, this stores the changes required to reach the required values, this then applied to each of the words.
The \verb|get_global_id| command takes the ID from the currently running thread, this allows a different value to be used for each exponent and allows the code to be run concurrently.

\section{First Experiment}
In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire. It provided functionality to easily present questions and record their responses. However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality an extra solution was required. This was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form. This allowed the re-sampling of matches each time a user submitted a response.

@@

Figure \ref{fig:GoogleAppScript} contains an interesting snippet from the script used in the experiment. Each time a user submitted their response the \verb|updateForm()| endpoint was called, that subsequently updated the questions for the next user. This aimed to keep the samplings fair as they are equally likely to appear when attacking the system.

\newpage

\section{MainExperiment}
In order to assess users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required. The front-end is developed in Javascript with a Python-Flask backend that acts as the webpages functionality. A number of end points are exposed like \verb|get_audio| or \verb|get_words| that are requested and displayed on the front-end.

One of the main problems encountered was the handling of each user's session. Initially during testing it was noted that changes in one end-point if timed correctly would overwrite the progress of another, this is commonly known as a ``Lost update''. This was due to the user session being stored in the \verb|session| cookie. When sending off a request the session cookie is included in the header, the code will then utilise the data within the cookie to make decision and alter state, the updated state is then returned as a cookie in the response. If, however, another request is executed before the first has completed, the second request is using the context of the first request and, thus, any alterations made by the first will be completely lost.

@@

Figure \ref{fig:cookie} shows this problem visually. As it can be seen the response cookie $c_2$ is based off the old data of $c$. When $c_2$ is eventually returned it will remove the progress of $c_1$. To keep the complexity of the backend as low as possible it was opted to solve this problem by restricting the user via the UI. When a button was clicked all other operations were disabled until a response was received. This stopped the possibility of sending off another request while another is still processing.

In order to collate data for results later in the process state had to be saved. One potential solution would be to format the data and save it as a .csv file. However, this is a static way of data persistence and would require alteration every time the data schema was modified. The chosen solution utilized a python object serialization library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}. This library saves the instance of a class as a file. This file then can be used to load the instance of the class back into the program. This allows changes to the object to filter down through the program and keeps the design of the application fluid. For example, after initial feedback gathered about the application it was decided that a inclusion of `Round times' would be a useful addition. Edits were made to the \verb|experiment| class and the changes propagated through the application, no changes were needed on the save functionality. To distinguish between old and new save formats a version number was used.
